Survivable Set Connectivity

### 2015-05-11 draft.tex
minor changes

Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e'$ in the tree is included is at most 
\begin{align}
height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 \\
&= O(\log^3 n) y_{e'} 
\end{align}
This is because $height(T) = O(\log n)$, $\tau' = O(\log n)$, and $q$ takes $O(\log n)$ possible values. So the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.

>>>>

So the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.
